\documentclass[a4 paper,12pt]{article}\usepackage{xepersian}
\settextfont{Yas}
\setdigitfont{Yas}
\title{حروف چینی با نرم افزارلاتک}
\author{شهریار شمسی}
\date{\today}
\begin{document}
\maketitle



\noindent
نام : شهریار  نام خانوادگی : شمسی          شماره دانشجویی : 963930790 \\ دانشچوی رشته مهندسی کامپیوتر  \\ درس:  روش پژوهش و ارائه  \\ استاد محترم : جناب آقای دکتر رضوی \\
پروژه لاتک صفحات 102 تا 105  کتاب :                                                                                                                                                                                                                                                                                                                                                          \lr{E-search Methodes strategies}\


       

\begin{latin}
\vspace{0.1cm}

\vspace{0.1cm}
\vspace{0.1cm}

\vspace{0.1cm}

                CHAPTER EIGHT

\vspace{0.1cm}

\vspace{0.1cm}
\vspace{0.1cm}

\vspace{0.1cm}

                  FOCUS GROUPS

\vspace{0.1cm}

\vspace{0.1cm}
\vspace{0.1cm}

\vspace{0.1cm}
\vspace{0.1cm}


\noindent
                 An effective way of getting at the answers to questions that are not yet  well defined and the topic is not yet  well understood is through the use of focus groups. A focus group is a unique kind of interview,  in that it draws  data from a number ot people in a man­  ner that is nonquantitative (Neuman, 2000). Ofcourse, before conducting a Net-based focus group, e-researchers will need to ask themselves two questions. First, why choose a focus group interview over other kinds of methods? Second, why choose a Net-based focus group over a face-to-face focus group?
\vspace{0.1cm}

\vspace{0.1cm}
\vspace{0.1cm}

\vspace{0.1cm}
\vspace{0.1cm}


With respect to the first  question, the  nature of the research question should die­ tate  the  type  of research  that  is conducted (Mertens, 1998), Focus  groups are  com­ monly used  to define the  research topic and  the  research questions  (Fowle, 1995), Focus groups can  be used  for  both exploration and  confirmation and are  particularly effective  for collecting data about  attitudes, perceptions, and opinions.  Focus groups can  be especially  useful  for revealing  the  complexities of the problem, but can  also be useful  for evaluation purposes (most  often program evaluations) to  identify strengths,weaknesses, weaknesses, and  needed improvements. They are not intended to reach a consensus among participants, to determine a plan of action, or to generate solutions and deei­ sions. Rather, they  stimulate in-depth exploration of a topic when  little is known  about the phenomenon of interest (Stewart and Shamdasani,1998) As such, focus groups are particularly effective for gaining a more in-depth understanding  of  the topie, and, hence, a better definition of the  research question(). Thus, when beginning to explore a topic for  investigation within the field of education, focus groups can  effectively nar­ row  the topic, define the research question, and  identify the delimitations of the study.

\vspace{0.1cm}
\vspace{0.1cm}

\vspace{0.1cm}
\vspace{0.1cm}
\noindent
The  main assumption embedded in  the  focus group method is a belief that the
decisions we make are  socially   constructed  and  grow out  of discussions with other people (Patton,  1987). Hence, focus groups are  effective at  gathering data  in  a social context, in  which  individual members consider their opinions against the opinions of others. While the focus  group interview was originally  inspired in the  1950s as a way of obtaining consumer product preferences, this  technique eventually  found  its way into educational and  social science research  methodology  It has  been shown  to have the capacity  to garner rich  and credible qualitative  data.  Further, according to Patton (1990), focus group interviews provide quality  controls on  data  collection, as partici­ pants  tend to question and eliminate false or extreme views, The result  is a tendency to focus on the most  important topics and issues and  to assess the extent to which  a rel­ atively  consistent, shared view exsts among participants-as well as identifying incon srstent views.
\vspace{0.1cm}
\vspace{0.1cm}

\vspace{0.1cm}
\vspace{0.1cm}
\noindent
This method is called  a focus group interview  because  it is focused in two ways. First, the group  participants are similar in some way (e.g., they have similar experiences of the  topic being  investigated). Second, the  purpose is to gather data about  a single topic (or  a narrow   range  of topics). They are  most  often  guided  by open-ended dis­ cussion questions proposed by  the  researcher, with  an emphasis on  gaining  insights through group opinions rather than  on specific facts. This format is a convenient way to accumulate the  individual  knowledge of the  members and  to inspire insights and
solutions that  are difficult  to achieve  with other interview methods.A distinct advan­ tage of focus groups is that  they allow  respondents to react to and  build  on responses. The result  can  be a synergistic and  dynamic effect on  group behavior, often resulting in data or ideas  that  might  not have been collected in individual interviews (Stewart and Shamdasani, 1998). Moreover, because focus groups  tend  to provide checks  and  bal­ ances among group  members to eliminate false or extreme views, it is fairly easy for the researcher to assess  the  extent ofconsistent and  shared views  (Patton, 1990), Given these advantages, according to Glesne and Peskin  (1992), interviewing a group of peo­ ple  on  a focused topic can  be a powerful way  to collect  data.  However, it  should be stressed  that  focus groups  do not  represent feedback from a randomly selected  popu­ lation, but  from purposely  selected individuals. As such,  the  results from  focus group interviews should not  be generalized to other, larger populations.
\vspace{0.1cm}
\vspace{0.1cm}

\vspace{0.1cm}
\vspace{0.1cm}

\noindent
 Finally,  Net-based focus groups are  usually  selected  over face-to-face focus groups because  of the  need  to  involve individuals from   several  different geographic areas.  'The  travel  time  and  expense  of bringing geographically dispersed individuals together  is  often  prohibitive. The  Net  provides an  environment  whereby  the researcher can conduct a focus group cost-effectively
\vspace{0.1cm}
\vspace{0.1cm}

\vspace{0.1cm}
\vspace{0.1cm}
THE DIFFERENT KINDS OF NET-BASED FOCUS GROUPS\\

\noindent
Net-based focus  groups  can  be conducted on the  Internet either synchronously or asynchronously and  with text-based software and/or audio and  video software.  'Table
8.I  provides examples  of  various kinds   of Net-based focus groups   classified   by asynchronous, synchronous, text-based, and  non-text-based distinctions. As this  table illustrates,  there are four kinds of Net-based focus groups: synchronous and text-based; synchronous and  audio- and/or video-based; asynchronous and  text-based; asynchro­ nous and  audio- and/or video-based. 
\vspace{0.1cm}


  

\vspace{0.1cm}

\vspace{0.1cm}


\vspace{0.1cm}

\vspace{0.1cm}

TABLE 8.1 Samples of Net-Based Systems to Support Focus  Groups\\
\begin{tabular}{cccc}\hline
                      &                             &syncronaise      & asyncronaise\\\hline
TEXT- BASED &                             & NET- METTING & Majordemo    \\\hline 
                      &                             &     ICQ              & FirstClass       \\\hline
                      &                             & FirstClass         & WebCT            \\\hline
                      &                             &   WebCT           & Email Groups    \\\hline 
AUDIO - AND/OR VIDEO BASED   &   Central           & Central             \\\hline
                      &                             &   Latitude          &   Latitude            \\\hline
                      &                             &  NET-METTING  &                            \\\hline



\end{tabular}

\vspace{0.1cm}
\vspace{0.1cm}
\vspace{0.1cm}


The  combination of media  used in the  focus group  process  makes it difficult  to generalize  about the  characteristics of all focus  groups.  Nevertheless, what uniquely differentiates a focus  group from an interview  is the  capacity of rarticipants  to share and build  on  the  comments and  concerns of other participants.Prior to the  Internet, there was no such  thing as an asynchronous focus group; although one  could conceive of mail-based focus  groups, researchers did  not  actively  use  the  technique. The pre­ dominant forms of asynchronous communication on the  Internet have been text-based email  and computer conferencing. Currently we are seeing a rapidly evolving selection of  more media-rich forms of asynchronous communication to  conduet Net-based focus  groups  (e.g.,  www.wimba.com), On the  synchronous side,  text-based chats are the  most common and  accessible  way to conduct real-time focus groups. This mode of interaction uses software such as ICQ,  NetMeeting, or one of the numerous Java-based Web chat  software  programs to share  the  comments of participants as they type. Text can be enhanced by viewing objects, sharing  applications, or sharing  a common space through text-based virtual reality (VR) systems such as MOO or  MUD (for frequently asked  questions about  MUDs and  MOO see: http://www.faqs.org/faqs/games/mud­ faq/part/) or  through two-  or  three-dimensional VR environments such  as  Palace (e.g.,  www.thepalace.com) or  virtual   worlds  (e.g., www.worlds.net).Finally, focus groups  can  be conducted  using  audio  or  video conferencing. Until   recently, the required  software,  end-user  hardware,  and  bandwidth  have prevented  use of these richer and more natural  forms  of communication on  the  Net.\\
 However,  the  develop­ ment  of multisite  audio  and  video  conferencing systems (see  www.microsoft.com/ windows/netmeeting/ and www.eentra.com) and  the  availability of  high-speed con­ nections at home and  in the workplace promise  increased use of media-rich, synchro­ nous  forms of Net-based  focus  groups.
Currently, most  Net-based  focus groups  are conducted using  text-based  asyn­ chronous or synchronous software.  Accordingly, this  chapter focuses  on  Net-based textual  focus groups. As broadband services proliferate and become more  widely avail­ able and affordable, we will likely see  an  increase  in synchronous and  asynchronous Net-based video and/or audio  focus groups. As these multimedia services are added to Net-based focus groups, they will tend to be more like face-to-face focus groups. Con­ sequently, conducting face-to-face focus groups will  become increasingly relevant and useful to e-researchers who use video- and audio-conferencing focus groups.

\noindent
  ADVANTAGES AND  DISADVANTAGES OF FACE-TO-FACE VERSUS  NET-BASED  FOCUS GROUPS\\
\vspace{0.1cm}

\noindent
Only recently have researchers been able to use the  Internet to conduct educationally related focus groups. Net-based focus groups offer both  speed and reduced cost  (Van Nuys,  1999) While Net-based focus groups are currently in the  exploration and  devel­ opment  stage, they appear to be especially effective at removing certain barriers that many  researchers experience when conducting face-to-face focus groups. In particular, they can  reduce or eliminate  participation and  cost  barriers. For example, if the  e­-researcher and the  participants are  geographically dispered,  Net-based  focus groups allow  them   to participate from their homes and/or offices, thus  travel   expenses are eliminated. Van Nuys's cost analysis indicates that, in addition to travel savings, there
is also  about a 20 percent cost savings in conducting the  focus group, compared to face­ to-face  focus groups. For example, such costs  as  food,  beverages, and room   rental would  not be incurred in a Net-based focus group. In addition to this  benefit, online discussions can  be automatically archived, eliminating the  transcription process and
transcriber interpretation error.
\vspace{0.1cm}


Finally, Net-based focus groups may also  reduce  power struggles that often occur in face-to-face focus groups asa result of conflicting opinions when there are perceived status differences among participants (Patton, 1990).  However, it  is not  necessary  for Net-based focus group participants to reveal  their real  identities to other members of the group. Given this ability  to provide an alias for each participant (depending on  the medium) and that Net-based focus groups have  the  ability  to join  geographically dis­ persed participants (thus reducing the  likelihood of participants knowing each  other), power struggles and confidentiality problems can  be reduced if not  eliminated.
\vspace{0.1cm}

\vspace{0.1cm}
Not with standing  these advantages, early   explorations with   Net-based focus
groups have met with  mixed results with  respect to the  quality of the  data collected. Van  Nuys (199) has  observed, for example, that  a drawback  of text-based asynchro­ nous focus groups is that  quite often there is less  depth in the participants' responses as  well as a loss of paralinguistic cues  (e.g., facial  expression, body posture, gesture, physical distance from  the  interlocutor, intonation pattern, and  volume). Paralinguis­ tie cues,  in particular, are considered to be a very  valuable source of data  in face-to-face
focus groups-in  addition to what is said.  Furthermore, Van Nuys notes that Net­
based focus groups tend not to be effective for  exploring complex concepts. Alterna­
tively, Van  Nuys has  also observed that in  text-based asynchronous focus groups, participants tend to speak more freely,  since they cannot see others. In particular, the responses may  be more objective, as participants tend to get  straight to the  point and not  to  "beat  around the  bush" when  they   are  not face-to-face, since responses are typed,  rather than spoken.



\end{latin}
\noindent
این گزارش و جدول پیوست آن همه   توسط نرم افزار لاتک تهیه شده است.
\end{document}



\end{document}

